Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-08 MS/ms.Rmd
Fix table legend

```{r tablea, echo = FALSE, tab.cap = "Common effect sizes, associated sampling variances and notes on when they might be used. Note that for log odds ratio a continuity correction is applied (i.e., 0.5) to each proportion. In addition, a correction factor, J (1-3 ), is applied to the standardised to correct for small sample effects"}

>>>>

```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used. Note that that a correction factor, J = 1 - (3 /  (4(N1 + N2 - 2) - 1)), is applied to the SMD to correct for small sample effects"}
